---
output:
  word_document: default
  html_document: default
---
Setting the Seed:

This ensures the reproducibility of the random numbers generated.
```{r}
set.seed(100)
```

Generating Random Values:

Generates 100 random values from a normal distribution with mean 7 and standard deviation 4.
```{r}
temp <- c(rnorm(100, mean = 7, sd = 4))
```

Setting Names:

Assigns names to each element in the temp vector, labeling them as "D-1" to "D-100".
```{r}
names(temp) <- paste0("D-", 1:100)
```

Rounding Values:

```{r}
temp <- round(temp, digits = 1)
```
Rounds each value in the temp vector to one decimal place.

Calculating Days with Temperature Greater than the Mean:
```{r}
gt_mean <- mean(temp)
gt_temp <- temp[temp > gt_mean]
length(gt_temp)
```

Calculates the mean of the temp vector and finds how many days have temperatures above this mean.

Finding Maximum Temperature Day:
```{r}
max_temp <- max(temp)
n = names(temp)[match(max_temp, temp)]
cat("The max temp was on day", n, "with a value of", max_temp)
```
Identifies the day with the maximum temperature and prints it.

Finding Minimum Temperature Day:

```{r}
min_temp <- min(temp)
n = names(temp)[match(min_temp, temp)]
cat("The min temp was on day", n, "with a value of", min_temp)
```
Identifies the day with the minimum temperature and prints it.

Creating Warnings Vector:
```{r}

warnings <- c(ifelse(temp <= 4.0, 'Warning', 'Normal'))
```
Creates a vector that labels days as "Warning" if the temperature is less than or equal to 4.0, otherwise "Normal".

Counting Warning Days:

```{r}
warn_days <- c(warnings == "Warning")
disp <- temp[warn_days]
disp_days = length(disp)
cat("The number of days the warnings were in operation =", disp_days)
```
Counts and displays the number of days when the temperature warning was in place.

Displaying Warning Days:
```{r}
ww = names(temp)[match(disp, temp)]
ww
```
Lists the days when the temperature warning was in place.

Tabular Display of Warnings:

```{r}
tw <- table(warnings)
tw
```
Displays the count of "Warning" and "Normal" days in a table format.

Finding Maximum Sequence of Warnings:
```{r}
len <- rle(warnings)
len1 <- tapply(len$lengths, len$values, max)
disp_warn <- len1[2]
disp_norm <- len1[1]
cat("The maximum run of days with warnings was", disp_warn, "\nThe maximum run of days without warnings was", disp_norm)
```
Uses the rle() function to find the longest sequence of consecutive "Warning" and "Normal" days.